---
title: "RMarkdown lesson"
output: html_document
---

```{r setup, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r chunk1, message=FALSE}
# install.packages("readr")
library(readr)
```

## Introduction

The data we are going to use in this exercise was provided by Craig Tweedie (2009) and was downloaded from the [NSF Arctic data Center](https://arcticdata.io/catalog/view/doi:10.18739/A25T3FZ8X)

- read in data

```{r , message=FALSE}
bg_chem <-read_csv("data/BGchem2008data.csv")
```


## Analysis

We are interested in nutrient concentrations over the whole water column. So we calculate the mean value of nutrients of interest (nitrate, nitrite, and phosphate).

```{r}
nitrate <- mean(bg_chem$NO3)
nitrite <- mean(bg_chem$NO2)
amm <- mean(bg_chem$NH4)
phos <- mean(bg_chem$P)
```

- calculate mean Redfield ratio

```{r}
ratio <- (nitrate+nitrite+amm)/phos
```

We calculated the Redfield ratio to be `r round(ratio)`

- plot Redfield ratio

```{r, echo = FALSE}
plot(bg_chem$P, bg_chem$NO2 + bg_chem$NO3 + bg_chem$NH4)
```

